Applying Spatio-temporal Scan Statistics and Spatial Autocorrelation Statistics to identify Covid-19 clusters in the world.

### 2021-01-12 Notebooks/paper_covid.rmd
Update paper_covid.rmd

  The Poisson Scan Statistic calculated for the number of cumulative cases identified the duration of emerging *clusters* in the number of infections throughout the year, in a comparison of a timeline of events that occurred in the pandemic $\!\!^3$ and the observed *clusters*, since March 25th the US was identified as an emerging *cluster* by the Scan Statistic and one day later turned out to be the country with most cases of Covid-19 in the World, in May 22th Brazil was identified as a *cluster* and in the same day surpassed Russia turning out to be the 2 $\!\!^n\!^d$ country with most cases in the world. Other patterns can be verified when comparing results given by the Scan Statistics against the locations identified as HH and HL *clusters* in the Boxmaps of infections per inhabitants **(Picture 4)**, all *clusters* of the Scan Statistic were also HH or HL *clusters* in the months they have been identified (October, November and December).

>>>>

  The Poisson Scan Statistic calculated for the number of cumulative cases identified the duration of emerging *clusters* in the number of infections throughout the year, in a comparison between a timeline of events that occurred in the pandemic $\!\!^3$ and the observed *clusters*, since March 25th the US was identified as an emerging *cluster* by the Scan Statistic and one day later turned out to be the country with most cases of Covid-19 in the World, in May 22th Brazil was identified as a *cluster* and in the same day surpassed Russia turning out to be the 2 $\!\!^n\!^d$ country with most cases in the world. Other patterns can be verified when comparing results given by the Scan Statistics against the locations identified as HH and HL *clusters* in the Boxmaps of infections per inhabitants **(Picture 4)**, all *clusters* of the Scan Statistic were also HH or HL *clusters* in the months they have been identified (October, November and December).
